---
title: "Regression Project"
author: "Moises Sales"
date: "November 2, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
if(!require("rglwidget")) {install.packages("rglwidget");require("rglwidget")}
data <- read.csv(file = "http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep = "",header = TRUE)
```
```{r}
plot(SIMS~ARM,data=data)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point()
```
```{r}
basicNN + geom_point(aes(col=ARM)) 
```
```{r}
cor(SIMS~ARM,data=data)
```
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
```{r}
basicNN + geom_point(aes(col=ARM)) + geom_smooth(method=lm)
``` 

```{r}
x=data.frame(GRIP=94, ARM=88)
predict.lm(model.1,x,interval = "prediction")
```

The 95% predictions intervals are between 0.706-3.13

Now for SIMs the function of GRIP


```{r}
plot(SIMS~GRIP,data=data)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
```{r}
basicNN + geom_point()
```
```{r}
basicNN + geom_point(aes(col=GRIP)) 
```
```{r}
cor(SIMS~GRIP,data=data)
```
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
```{r}
basicNN + geom_point(aes(col=GRIP)) + geom_smooth(method=lm)
``` 

```{r}
x=data.frame(GRIP=94, ARM=88)
predict.lm(model.2,x,interval = "prediction")
```

The 95% predictions intervals are between -0.536-2.03

Now for the SIMs function of ARM+GRIP

```{r}
plot(SIMS~ARM+GRIP,data=data,xlab = "ARM+GRIP")
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM+GRIP))
```
```{r}
basicNN + geom_point()
```
```{r}
basicNN + geom_point(aes(col=ARM+GRIP)) 
```
```{r}
cor(SIMS~ARM+GRIP,data=data)
```
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```
```{r}
basicNN + geom_point(aes(col=ARM+GRIP)) + geom_smooth(method=lm)
``` 

```{r}
x=data.frame(GRIP=94, ARM=88)
predict.lm(model.3,x,interval = "prediction")
```

```{r}
a=anova(model.1,model.3)
print(a)
str(a)
```

$H_0$: We fail to reject the null hypothesis showing that there is no difference between arm strength vs. arm+grip strength

$H_A$: We reject the null hypothesis showing that there is a difference between arm strength vs arm+grip strength

In this data test we find our P-value to be 4.994e-06 < 0.05 so we fail to reject the null hypothesis thus we can conclude that there is no difference between arm strength and arm plus grip strength. We may also conclude that our overall simulation for arm+grip strenght is a better model prediction than our arm strength model.








